---
title: "Atividade 01"
author: "Fagner Sutel de Moura"
date: "3/17/2024"
output: html_document
---

```{r, warning=FALSE, message=FALSE}
library(readxl)
ds <- read_excel("data partly.xlsx") #replace it with your path.
```

# Rename columns, since they are in Chinese (on the original dataset)
```{r, warning=FALSE, message=FALSE}
ds[,34] = 6 -ds[, 34]
colnames(ds) <- c("id",
                  "time_spent",
                  "gender",
                  "age_group",
                  "driving_experience_years",
                  "driving_experience_years_group",
                  "annual_mileage",
                  "monthly_salary",
                  "education_level",
                  "other_insurance",
                  "have_accident",
                  "accident_speed_highway",
                  "speed_fine_highway",
                  "speed_bellow_limit",
                  "ATT1", "SN1", "IN1",
                  "SN2", "BH1", "PBC1",
                  "ATT3", "RP1", "IN2",
                  "BH2", "ATT2", "RP2",
                  "SN3", "PBC2", "SN4",
                  "RP3", "attention_check",
                  "BH3", "PBC3", "ATT4",
                  "IN3", "BH4", "PBC4")

ds = ds[complete.cases(ds[, c("ATT1","ATT2","ATT3", "ATT4"),]), ]
```


```{r, warning=FALSE, message=FALSE}
sub = ds[, c("ATT1","ATT2","ATT3", "ATT4")]
```

# Ômega | Cronbach’s Alpha 

```{r, warning=FALSE, message=FALSE}
psych::omega(sub)
```

# Alpha

```{r, warning=FALSE, message=FALSE}
psych::alpha(sub)
```

# Correlation
```{r, warning=FALSE, message=FALSE}
library(ggcorrplot)

correlation_matrix <- cor(sub)
ggcorrplot(correlation_matrix, type = "lower", lab = TRUE)
```

# Polychoric Matrix  

```{r, warning=FALSE, message=FALSE}
psych::polychoric(sub)
```
# scaleStructure  

```{r, warning=FALSE, message=FALSE}
ufs::scaleStructure(dat = ds,
                    items = c("ATT1","ATT2","ATT3", "ATT4"))
```

```{r, warning=FALSE, message=FALSE}
dfnum = ds
#gender --- respondent gender
ds$gender <- factor(ds$gender,
                    levels = c(1,2),
                    labels = c("Female","Male"))
#age_group --- respondent age group
ds$age_group <- ordered(ds$age_group,
                        levels = c(1:5),
                        labels = c("18-30","31-40","41-50","51-60",">60"))
#driving_experience_years --- driving experience in years
#driving_experience_years_group --- driving experience (years group
ds$driving_experience_years_group <- ordered(ds$driving_experience_years_group,
                                             levels = c(1:4),
                                             labels = c(" 1",
                                                        "2–5",
                                                        "6–10",
                                                        " 11"))
#annual_mileage --- Annual mileage (km)
ds$annual_mileage <- ordered(ds$annual_mileage, levels = c(1:5),
                             labels = c("<10,000",
                                        "10,000–20,000",
                                        "20,000–40,000",
                                        "40,000–60,000",
                                        " 60000"))
#monthly_salary --- Monthly income (Renminbi; currency of PR China )
ds$monthly_salary <- ordered(ds$monthly_salary, levels = c(1:3),
                             labels = c(" 5,000",
                                        "5,000–10,000",
                                        " 10,000"))
#education_level --- respondent education level
ds$education_level <- ordered(ds$education_level, levels = c(1:3),
                              labels = c("Lower secondary or below",
                                         "Secondary education",
                                         "Tertiary education"))
#other_insurance --- Insurance other than mandatory insurance
ds$other_insurance <- factor(ds$other_insurance,
                             levels = c(1,2),
                             labels = c("Yes","No"))
#have_accident --- Accident experience
ds$have_accident <- factor(ds$have_accident,
                           levels = c(1,2),
                           labels = c("Yes","No"))
#accident_speed_highway --- Accident experience in the highway due to high speed
ds$accident_speed_highway <- factor(ds$accident_speed_highway,
                                    levels = c(1,2),
                                    labels = c("Yes","No"))
#speed_fine_highway --- Fine experience in the highway due to high speed
ds$speed_fine_highway <- factor(ds$speed_fine_highway,
                                levels = c(1,2),
                                labels = c("Yes","No"))
#speed_bellow_limit --- Low-speed driving frequency
ds$speed_bellow_limit <- ordered(ds$speed_bellow_limit,
                                 levels = c(1:5),
                                 labels = c("Never", "Rarely drive at low-speed", "Sometimes / occasionally dive
  at low-speed", "Often dive at low-speed", "Always dive at low-speed"))
```


```{r, warning=FALSE, message=FALSE}
# ds$ATT1 <- ordered(ds$ATT1, levels = c(1:5),
#                               labels = c("Definitely disapprove", "Disapprove", "Neutral", "Approve",
#              "Definitely approve"))
# ds$ATT2 <- ordered(ds$ATT2, levels = c(1:5),
#                               labels = c("Definitely disapprove", "Disapprove", "Neutral", "Approve",
#              "Definitely approve"))
# ds$ATT3 <- ordered(ds$ATT3, levels = c(1:5),
#                               labels = c("Definitely disapprove", "Disapprove", "Neutral", "Approve",
#              "Definitely approve"))
# ds$ATT4 <- ordered(ds$ATT4, levels = c(1:5),
#                               labels = c("Definitely disapprove", "Disapprove", "Neutral", "Approve",
#              "Definitely approve"))
```


```{r, warning=FALSE, message=FALSE}
att_items <- paste0("ATT",1:4)
sn_items <- paste0("SN",1:4)
pbc_items <- paste0("PBC",1:4)
in_items <- paste0("IN",1:3)
bh_items <- paste0("BH",1:4)
rp_items <- paste0("RP",1:3)
#make the vector c(att_items, sn_items, pbc_items, in_items, bh_items, rp_items)
#as ordered factors with levels from 1-5 with labels "Definitely disapprove"
#to "Definitely approve"
 
 
ds[,c(att_items, sn_items, pbc_items, in_items, bh_items, rp_items)] <- lapply(
  ds[,c(att_items, sn_items, pbc_items, in_items, bh_items, rp_items)],ordered,
  levels = 1:5,
  labels = c("Definitely disapprove", "Disapprove", "Neutral", "Approve",
             "Definitely approve"))
class(ds$ATT1)
```

The scaleStructure function (which was originally called scaleReliability) computes a number  of measures to assess scale reliability and internal consistency. Note that to compute omega, the MBESS and/or the psych packages need to be installed, which are suggested packages and  therefore should be installed separately (i.e. won't be installed automatically). 


Omega
 
The omega (ω) coefficient is also a reliability measure of internal consistency. ω represents an estimate of the general factor saturation of a test that was proposed by McDonald. (Zinbarg et al. 2005)  compare McDonald’s Omega to Cronbach’s α and Revelle’s β
 
They conclude that omega is the best estimate (Zinbarg et al. 2006). 
 
A very handy way to calculate McDonald’s ω is to use the scaleReliability() function from the serfriendlyscience package (which also provides  Cronbach’s α and the Greatest Lower Bound (GLB) estimate which is also a very good and innovative measure of reliability) (see also Peters 2014).


```{r, warning=FALSE, message=FALSE}

```


```{r, warning=FALSE, message=FALSE}
ufs::scaleStructure(dat = ds,
                    items = c("ATT1","ATT2","ATT3", "ATT4"))
```



# 1.4 Correlations among Items 

```{r, warning=FALSE, message=FALSE}
library(rio)
# https://rpubs.com/asghar_minaei/857065
dfcor <- dfnum[, c("ATT1","ATT2","ATT3", "ATT4")]
dfcor
```

# Especificar modelo  

```{r, warning=FALSE, message=FALSE}
mod.one.fCat <- 'psyctcsm =~ ATT1 +  ATT2 +  ATT3 +  ATT4'
mod.one.fCat
```

# Estimar modelo  

```{r, warning=FALSE, message=FALSE}
library(lavaan)
fit.one.fCat <- cfa(mod.one.fCat, data=dfcor, std.lv=TRUE, ordered=T, estimator='WLSMV')
```

# Resultados  

```{r, warning=FALSE, message=FALSE}
summary(fit.one.fCat, fit.measures=TRUE, standardized=TRUE)
```

# 1.5 Spearman-Brown Prophecy Formula  

```{r, warning=FALSE, message=FALSE}
#install.packages("splithalf")
library(splithalfr)
# Calculate coefficient based on ICC, two-way, random effects, absolute agreement, single rater
spearman_brown(dfcor[, "ATT1"], dfcor[, "ATT2"])
#           ATT2
# ATT1 0.771888
library(psychometric)
```

Details

Nlength represents a ratio of new to original. If the new test has 10 items, and the original test has 5 items, Nlength is 2. Likewise, if the original test has 5 items, and the new test has 10 items, Nlength is .5. In general, researchers should aim for reliabilities > .9.
 
SBrel is used to address the question, what if I increased/decreased my test length? What will the new reliability be? This is used when computing split-half reliabilities and when when concerned about reducing test length.
SBlength is used to address the question, how long must my test be (in relation to the original test) in order to achieve a desired reliability?
The formulae for each are:
$$rxxp <- Nlength*rxx/(1+(Nlength-1)*rxx)$$

$$ N <- rxxp*(1-rxx)/(rxx*(1-rxxp))$$

Nlength = tamanho do novo dataset/ tamanho do antigo dataset (10/5)=2



```{r, warning=FALSE, message=FALSE}


#SBrel(Nlength, rxx)
SBrel(374, .77)
# [1] 0.999202
#SBlength(rxxp, rxx)
nrow(dfcor)
# [1] 374
SBlength(.85, .77)*nrow(dfcor)
# [1] 633.0476

```
